### 2016-07-22 inst/vign/name_cleaning.Rmd
bump dev version, updated name cleaning vignette fix #549 udpated pkg level man file with author and bold taxizesoap reference started to update news

This vignette covers various options for programmatic name cleaning.

@@

In reality it is unlikely you'll know which row you want, unless perhaps you 
just one one result from each query, regardless of what it is.

@@

@@

>>>>

This vignette covers some options for programmatic name cleaning.

@@

In reality it is unlikely you'll know which row you want, unless perhaps you
just want one result from each query, regardless of what it is.

@@

## as.* methods

All `get_*()` functions have associated `as.*()` functions (e.g., `get_tsn()` and `as.tsn()`).

Many `taxize` functions use taxonomic identifier classes (S3 objects) that are the output
of `get_*()` functions. `as.*()` methods make it easy to make the required S3 taxonomic
identifier classes if you already know the identifier. For example:

Already a tsn, returns the same

```{r}
as.tsn(get_tsn("Quercus douglasii"))
```

numeric

```{r}
as.tsn(c(19322, 129313, 506198))
```

And you can do the same for character, or list inputs - depending on the data source.

The above `as.tsn()` examples have the parameter `check = TRUE`, meaning we ping the 
data source web service to make sure the identifier exists. You can skip that check 
if you like by setting `check = FALSE`, and the result is returned much faster:

```{r}
as.tsn(c("19322","129313","506198"), check = FALSE)
```

With the output of `as.*()` methods, you can then proceed with other `taxize` functions.

@@

## Other functions

Some other functions in `taxize` use `get_*()` functions internally (e.g., `classification()`),
but you can can generally pass on parameters to the `get_*()` functions internally.

## Feedback?

Let us know if you have ideas for better ways to do programmatic name cleaning at 
<https://github.com/ropensci/taxize/issues> or <https://discuss.ropensci.org/> !
